---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# playbase

<!-- badges: start -->
[![R package check](https://github.com/bigomics/playbase/actions/workflows/r.yml/badge.svg)](https://github.com/bigomics/playbase/actions/workflows/r.yml)
<!-- badges: end -->

The `playbase´ package contains the core back-end functionality for the OmicsPlayground. This package allows you to run, develop, and test any essential functions used in the OmicsPlayground directly in the R console without needing to worry about the R Shiny front-end code.

## Installation

You can install the development version of playbase from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bigomics/playbase")
```

## Data upload

The first step in any OmicsPlayground analysis is to upload data which can be used to create a `pgx` object. The `pgx` object is basically the core data structure in the OmicsPlayground upon which most analysis and plotting functions operate.

```{r example}
library(playbase)

## example files can be accessed via the example_file() function
counts <- playbase::read_counts(playbase::example_file("counts.csv"))
samples <- playbase::read_samples(playbase::example_file("samples.csv"))
contrasts <- playbase::read_contrasts(playbase::example_file("contrasts.csv"))

## create a pgx object (new style)
#pgx <- playbase::create_pgx(counts, samples, contrasts)

## old style still works
#pgx <- playbase::pgx.createPGX(counts, samples, contrasts)

```

## Adding namespace


```{r namespace}
library(addns)
#addns::add_ns(path = "R/", packages = c("playbase"))
#adds::rm_imports(path = "R/")
```
